### 2019-12-16 ntuvars.tex
加入基本資訊

% author: Tz-Huan Huang [http://www.csie.ntu.edu.tw/~tzhuan]

% ----------------------------------------------------------------------------
% "THE CHOCOLATE-WARE LICENSE":
% Tz-Huan Huang wrote this file. As long as you retain this notice you
% can do whatever you want with this stuff. If we meet some day, and you think
% this stuff is worth it, you can buy me a chocolate in return Tz-Huan Huang
% ----------------------------------------------------------------------------

% Syntax: \var{English}{Chinese}
\university{National Taiwan University}{國立臺灣大學}
\college{College of Electrical Engineering and Computer Science}{電機資訊學院}
\institute{Department of Computer Science and Information Engineering}{資訊工程學系}
\title{A design of account-based stateless blockchain}{基於帳號的無狀態區塊鏈設計}
\author{CUN-ZHE CAI}{蔡存哲}
\studentid{R05922086}
\advisor{Shih-Wei Liao, Ph.D.}{廖世偉 博士}
\defenseyear{2020}{109}
\defensemonth{February}{2}
\defenseday{1}
\doi{doi:10.6342/NTU2017XXXXX}
\keywords{keyword}{關鍵字}

### 2020-04-20 abstract.tex
加上摘要

\begin{abstractzh}
基於區塊鏈的虛擬貨幣是一種點對點的交易系統，在此去中心化的系統中，每個節點都維護一個完整的賬本，其中記錄了所有賬戶的全部交易資料。這樣的系統具有不容易被竄改資料的特點，然而此種特性會使得所需要儲存的資料只增不減，經年累月下來，對單個節點的儲存容量要求只會越來越高，一旦個體維護的節點逐漸不勘負荷，將導致此區塊鏈的中心化程度逐步上升。

無狀態區塊鏈是一種針對以上問題的改進方案，它的每一筆交易中附上了合法性證明，使得節點不需要進入硬碟查找過往賬本資訊，只要驗證交易內附的證明即可，從而使節點所需儲存資訊大幅減少。

在本論文中，我們將討論以下兩點：第一，並無必要在每一筆交易都附上證明，只要快取部分訊息，一筆交易的合法性很可能由最近出現過的其他交易的合法性推知。第二，當區塊鏈發生分叉時，必須回到分叉點再產生新區塊的快取，為此我們設計了不可變的資料結構，使得快取能夠在各種情況下被快速計算。最後，進行實驗來瞭解數種快取策略與資料結構在不同工作量（workload）下的表現。

\bigbreak
\noindent \textbf{關鍵字：}{\, \makeatletter \@keywordszh \makeatother}
\end{abstractzh}

\begin{abstracten}
This thesis presents a benchmark for region of interest (ROI)
detection. ROI detection has many useful applications and many
algorithms have been proposed to automatically detect ROIs.
Unfortunately, due to the lack of benchmarks, these methods were
often tested on small data sets that are not available to others,
making fair comparisons of these methods difficult. Examples from
many fields have shown that repeatable experiments using published
benchmarks are crucial to the fast advancement of the fields. To
fill the gap, this thesis presents our design for a collaborative
game, called Photoshoot, to collect human ROI annotations for
constructing an ROI benchmark. With this game, we have gathered a
large number of annotations and fused them into aggregated ROI
models. We use these models to evaluate five ROI detection
algorithms quantitatively. Furthermore, by using the benchmark as
training data, learning-based ROI detection algorithms become
viable.

\bigbreak
\noindent \textbf{Keywords:}{\, \makeatletter \@keywordsen \makeatother}
\end{abstracten}

\begin{comment}
\category{I2.10}{Computing Methodologies}{Artificial Intelligence --
Vision and Scene Understanding} \category{H5.3}{Information
Systems}{Information Interfaces and Presentation (HCI) -- Web-based
Interaction.}

\terms{Design, Human factors, Performance.}

\keywords{Region of interest, Visual attention model, Web-based
games, Benchmarks.}
\end{comment}

### 2020-04-20 abstract.tex
摘要分行

@@
 \begin{abstractzh}
-基於區塊鏈的虛擬貨幣是一種點對點的交易系統，在此去中心化的系統中，每個節點都維護一個完整的賬本，其中記錄了所有賬戶的全部交易資料。這樣的系統具有不容易被竄改資料的特點，然而此種特性會使得所需要儲存的資料只增不減，經年累月下來，對單個節點的儲存容量要求只會越來越高，一旦個體維護的節點逐漸不勘負荷，將導致此區塊鏈的中心化程度逐步上升。
+基於區塊鏈的虛擬貨幣是一種點對點的交易系統，
+在此去中心化的系統中，
+每個節點都維護一個完整的賬本，
+其中記錄了所有賬戶的全部交易資料。
+這樣的系統具有不容易被竄改資料的特點，
+然而此種特性會使得所需要儲存的資料只增不減，
+經年累月下來，對單個節點的儲存容量要求只會越來越高，
+一旦個體維護的節點逐漸不勘負荷，
+將導致此區塊鏈的中心化程度逐步上升。
 
-無狀態區塊鏈是一種針對以上問題的改進方案，它的每一筆交易中附上了合法性證明，使得節點不需要進入硬碟查找過往賬本資訊，只要驗證交易內附的證明即可，從而使節點所需儲存資訊大幅減少。
+無狀態區塊鏈是一種針對以上問題的改進方案，
+它的每一筆交易中附上了合法性證明，
+使得節點不需要進入硬碟查找過往賬本資訊，
+只要驗證交易內附的證明即可，
+從而使節點所需儲存資訊大幅減少。
 
-在本論文中，我們將討論以下兩點：第一，並無必要在每一筆交易都附上證明，只要快取部分訊息，一筆交易的合法性很可能由最近出現過的其他交易的合法性推知。第二，當區塊鏈發生分叉時，必須回到分叉點再產生新區塊的快取，為此我們設計了不可變的資料結構，使得快取能夠在各種情況下被快速計算。最後，進行實驗來瞭解數種快取策略與資料結構在不同工作量（workload）下的表現。
+在本論文中，我們將討論以下兩點：
+第一，並無必要在每一筆交易都附上證明，
+只要快取部分訊息，
+一筆交易的合法性很可能由最近出現過的其他交易的合法性推知。
+第二，當區塊鏈發生分叉時，必須回到分叉點再產生新區塊的快取，
+為此我們設計了不可變的資料結構，
+使得快取能夠在各種情況下被快速計算。
+最後，進行實驗來瞭解數種快取策略與資料結構在不同工作量（workload）下的表現。
 

### 2020-05-11 ctapc/paper.tex
ctapc abstract, introduction 、紅黑樹加一張圖

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The Design of Shallow State Blockchain*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
Cryptocurrency based on blockchain is a peer to peer trading system. In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account. The system has the characteristics that it is very hard to tamper with the data. However, such characteristic only makes the data increase but do not decrease. Years after years, requirement to single node will get higher and higher. Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise.

Dealing with the issue, stateless blockchain is a promising approach. To be more specific, in this system, each transaction is attached with proof of validity. With this approach, there is no need for a node to access the disk to search past information of the ledger. Instead, node only verifies the proof attached to each transaction. Therefore, it will significantly reduce the space of data storage for each node.

In this paper, we will discuss the following two points.
First, it only need to cache part of information instead of attaching proof to each transaction. It is highly possible to infer the validity of a transaction from other valid transaction appearing recently. Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks. To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation. Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures.
\end{abstract}

\begin{IEEEkeywords}
blockchain, stateless blockchain, data structure
\end{IEEEkeywords}

\section{Introduction}
In 2008, Satoshi Nakamoto proposed the white paper of bitcoin. It is a new type of cryptocurrency system based on blockchain. In this system, each node maintain a complete ledger in order to attain the high degree of decentralization of entire system. However, as the data size of ledger got bigger and bigger, storage space of node increased yearly. Ten years later, it costs hundreds of GB storage space for a node to run some well-known cryptocurrency system, such as Bitcoin and Ethereum. Thus, it gradually make the nodes maintained by person overload. If we settle for second best by saving the information needed for verifying new block, such as UTXO in Bitcoin and world state in Ethereum, it still needs several or tens of GB for disk storage place. With this method, not only the storage space of disk is requested but also  I/O speed. Furthermore, it is too slow for traditional disk to access randomly. The speed of verifying a block on Ethereum can't keep up with the generation speed of blocks. It force the node maintainer on Ethereum to buy expensive solid-state disk, and it further cause the increase in operation cost of node.

To deal with the problem above, cryptocurrency communities start trying several solutions, and stateless blockchain is prospective one of them. It only need to store block header for each node on stateless blockchain. Nevertheless, each transaction must be attached with proof of validity. This approach significantly reduces the requirement of storage space. Furthermore, it is no need to search the validity of transaction on disk; namely, it drastically reduces the I/O time.

This paper proposes an imrpovement to stateless blockchain. We let the node on stateless blockchain reach a consensus to maintain a cache. If the payer of transaction appears in recent transaction, it is highly possible to infer the validity from cache. Hence, due to the omission of proof of validity, it reduces the size of transaction and the Internet traffic while broadcasting. However, how to maintain cache effectively becomes a new problem. When a new block append to the blockchain, there will be a correspondent cache. Nevertheless, there will also exist overlap on the blocks nearby. Therefore, we design persisted data structure for different cache strategies, such as the nearest k blocks and LRU, and we conduct an experiment to test their performance.

The remaining sections are arranged as follows. Section II narratives some related works, whereas section III describes the background of this paper and preliminary knowledge; section IV illuminates the design of stateless blockchain, including cache strategies and data structures used by cache; section V shows the design and results of experiment; section VI discusses future extensions to stateless blockchain, and concluding remarks are found in section VII.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2020-05-12 abstract.tex
背景寫一半
更新英文摘要

@@
 \bigbreak
-\noindent \textbf{關鍵字：}{\, \makeatletter \@keywordszh \makeatother}
+\noindent \textbf{關鍵字：區塊鏈、無狀態區塊鏈、快取、資料結構}{\, \makeatletter \@keywordszh \makeatother}
 \end{abstractzh}
@@
 \begin{abstracten}
-This thesis presents a benchmark for region of interest (ROI)
-detection. ROI detection has many useful applications and many
-algorithms have been proposed to automatically detect ROIs.
-Unfortunately, due to the lack of benchmarks, these methods were
-often tested on small data sets that are not available to others,
-making fair comparisons of these methods difficult. Examples from
-many fields have shown that repeatable experiments using published
-benchmarks are crucial to the fast advancement of the fields. To
-fill the gap, this thesis presents our design for a collaborative
-game, called Photoshoot, to collect human ROI annotations for
-constructing an ROI benchmark. With this game, we have gathered a
-large number of annotations and fused them into aggregated ROI
-models. We use these models to evaluate five ROI detection
-algorithms quantitatively. Furthermore, by using the benchmark as
-training data, learning-based ROI detection algorithms become
-viable.
+
+Cryptocurrency based on blockchain is a peer to peer trading system.
+In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account.
+The system has the characteristics that it is very hard to tamper with the data.
+However, such characteristic only makes the data increase but do not decrease.
+Years after years, requirement to single node will get higher and higher.
+Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise.
+
+Dealing with the issue, stateless blockchain is a promising approach.
+To be more specific, in this system, each transaction is attached with proof of validity.
+With this approach, there is no need for a node to access the disk to search past information of the ledger.
+Instead, node only verifies the proof attached to each transaction.
+Therefore, it will significantly reduce the space of data storage for each node.
+
+In this paper, we will discuss the following two points.
+First, it only need to cache part of information instead of attaching proof to each transaction.
+It is highly possible to infer the validity of a transaction from other valid transaction appearing recently.
+Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks.
+To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation.
+Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures.
 
 \bigbreak
-\noindent \textbf{Keywords:}{\, \makeatletter \@keywordsen \makeatother}
+\noindent \textbf{Keywords:blockchain, stateless blockchain, cache, data structure}{\, \makeatletter \@keywordsen \makeatother}
 \end{abstracten}

### 2020-05-13 ctapc/paper.tex
順序樹連續變化

@@
 Years after years, requirement to single node will get higher and higher.
-Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise.
+Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise
 
@@
 To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation.
-Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures.
+Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures
 \end{abstract}
@@
 
-\section{Ease of Use}
+\section{design}
+In order to reduce occupied space of the disk, it is necessary for a stateless blockchain to attach a proof to each transaction.
+However, this move will increase Internet traffic.
+Furthermore, to reduce the time of accessing disk, it will cost computational power for CPU to verify the proof.
+Compared to normal blockchain, stateless blockchain made some trade-offs.
+Regarding the purpose of shallow-state blockchain, the trade-offs are no longer all or nothing, which means that all transactions are attached with proofs or none of transactions are attached with proofs.
+It makes the degree of state storage adjustable.
+
+\subsection{shallow-state blockchain}
+In stateless blockchain, if payers and payees in some transactions are the same, the proofs in these transactions will be identical.
+It is obvious that the same proofs can be omitted in a block.
+Extended by this idea, if we cache the accounts’ information appearing in recent transactions, there is no need to verify the proof again when the accounts make transactions.
+To go a step further, if nodes on the Internet follow the same set of rules to record cache, it will reach a consensus that node knows whether to attach the proof.
+While broadcasting the block, nodes can get rid of unnecessary proofs, and then reduce internet traffic.
+
+\subsection{cache design}
+The problems mentioned above can be avoided by a simple design principle.
+Namely, each block has its own cache, and the content of cache depends on which chain the block is situated.
+Therefore, we turn a tree structure into a list, and it is definitely identical for the block on different nodes.
+If every node uses the same deterministic algorithm to compute the cache from this list, it can ensure that every node gets identical results of cache after verifying the same block.
+
+\subsection{persistent cache}
+In this part, we take another approach: every block retains its own cache.
+When a new block is about to append to the chain, it can directly use the cache of the previous block.
+Thus, there is no need to compute cache again.
+In other words, we adopt fully persistent data structure to store cache.
+Everytime the chain gets a new block, it creates a new version of cache.
+In this method, we have to delete the cache of older blocks, such as the block 20 blocks far from the newest one, in order to limit the size of cache to a certain range.
+Otherwise, it will run out of memory, and it will violate our design principle.
+Adopting this method leads to a new problem.
+If we duplicate the cache of the previous block, the space of cache will be proportional to the cache numbers that we didn’t delete.
+However, there is a high similarity of the cache in adjacent blocks.
+If we use appropriate data structure to have the cache shared by adjacent blocks, it will effectively increase space usage.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{../images/LRU.png}}
+\caption{Example of a figure caption.}
+\label{fig}
+\end{figure}
+
+% \begin{figure}[htbp]
+% \centerline{\includegraphics{../images/不可變紅黑樹.png}}
+% \caption{Example of a figure caption.}
+% \label{fig}
+% \end{figure}
 

### 2020-05-14 ctapc/paper.tex
未來工作

@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{../images/LRU.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
+\subsection{LRU}
+LRU is an acronym for “least recently used”.
+In this strategy, the size of cache is fixed.
+If a cache is full, it will discard a piece of data before inserting new data.
+The least recently used data are chosen by LRU strategy, and it will be discarded.
+The reasons why LRU has higher hit rate than FIFO are revealed by the history data of Ethereum.
+First, after an account spends money, it is highly possible that it will spend money again.
+Second, after an account receives money,  it is highly possible that it will spend money right away.
+Because LRU updates the using time of data, it is able to keep caching the data appearing frequently.
+However, FIFO only looks at the coming time of data.
+Even if some data appear frequently, they will be discarded sooner or later.
+From an abstract view, LRU is a data structure that supports two kinds of interface.
+\begin{itemize}
+\item get(key)
+\item put(key, value)
+\end{itemize}
+When executing get(key), LRU will determine whether the key exists. If the key exists, it will return the value and update its using time.
+When executing put(key, value), LRU will determine whether the space of LRU is full.
+If the space of LRU isn’t full, the key-value pair will be inserted to the space directly.
+If the space of LRU is full, LRU will find out the least recently used one in the cache and abandon it, and then insert the new key-value pair to it.
+The using time of the new key-value pair should be the latest.
+Corresponding to the situation of stateless blockchain, everytime when a new block appends to the chain, we have to compute the cache of the new block.
+In this time, a series of read and modify execution of accounts will turn into get and put.
+Key will be the address of account, and value will be the state of account.
+Finally, the underlying data structure of LRU will take the correspondent action.
 
-% \begin{figure}[htbp]
-% \centerline{\includegraphics{../images/不可變紅黑樹.png}}
-% \caption{Example of a figure caption.}
-% \label{fig}
-% \end{figure}
+\subsection{persistent LRU algorithm}
+Before discussing persistent LRU algorithms, we first observe how to efficiently implement LRU cache on software.
+Judging from several popular LRU libraries on github, interior data structures are all combinations of hash table and doubly linked list.
+While executing get, it will get the data by the pointer pointing to the node of list.
+Then, the node will move to the head of the list.
+While executing put, if cache hits, the value of node will be updated, and the node will move to the head of the list.
+If cache is not full, the cache value will be added to the head and the pointer will be put in the hash table.
+Instead, if the cache is full, pull out the tail node of the doubly linked list, and delete the old key in the hash table.
+Then, add cache value to the head and put the pointer in the hash table.
+We observed that there are two kinds of information that need to be recorded by LRU.
+\begin{enumerate}
+  \item find the value from key (key-value pair)
+  \item the order information of all keys
+\end{enumerate}
+In the implementation of combinations of hash table and doubly linked list, hash table is responsible for (1), and doubly linked list is responsible for (2).
+We observed that a doubly linked list records the order relationship naturally, and it doesn't even need to record the definite using time.
+There is one simple idea that we directly combine persistent-versioned alternatives of a hash table and a doubly linked list, and then we get a persistent LRU.
+Although there are mature alternatives for hash tables, it is hard to find such a thing for doubly linked lists.
+Thus, we need to use other persistent and efficient data structures to replace doubly linked lists. The things that an abstract doubly linked list can do are as follows.
+\begin{itemize}
+\item Update the using time of node to latest
+\item Delete the least recently used node
+\item Insert new node and update the using time of the node to latest
+\end{itemize}
+Following we will discuss how to use red-black tree to complete the above tasks and introduce our design of order tree, which is more efficient than red-black tree.
+
+\subsection{hash table + red-black tree}
+We tried to use red-black to record the order information.
+First, set a unique timestamp for every account.
+This timestamp is easy to access. For instance,
+it could be $block\_height * max\_tx\_in\_one\_block+ tx\_number$.
+Afterwards, build a red-black tree whose key is timestamp and value is account’s information. About hash table, the account's address is set as key and the correspondent timestamp is set as value.
+While executing get, it first gets the timestamp from the account's address in the hash table, and then gets the account’s information from the timestamp in the red-black tree.
+For example, in Fig 3.6, we first get the account’s timestamp, 243, from the hash table, and search 243 in red-black tree.
+After searching, it needs to update the using time.
+The specific operations are that modify the timestamp corresponding to the address in the hash table and remove the original node in red-black tree.
+Then, set the new timestamp as key.
+The put operation is similar to get operation.
+However, it needs to modify the account's information.
+Fig 3.6 shows the sharing structure of the persistent red-black tree.
+In this figure, the cache size is 8.
+In state 1, there are only 7 data.
+After that, state 2 insert 14 in it, and there are 8 data.
+State 3 insert 15 to state 2, and the cache is full.
+Therefore, it has to delete the data of minimum timestamp; that is, the red 7 at lower left corner will be deleted.
 

### 2020-05-14 ctapc/paper.tex
ctapc 補上 related work

@@
 
-\subsection{Maintaining the Integrity of the Specifications}
+\section{Related Work}
+\subsection{Utreexo}
+Utreexo~\cite{b1} applying the Merkle forest to  design a new accumulator.
+Based on this accumulator, the Utreexo node does not need to actually store all of the UTXO and is still able to verify the blocks.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+However, the bitcoin network has been around for years, and it's not realistic to drastically modify the protocol so that all nodes become stateless.
+Utreexo proposes that a bridge node could be used as an intermediary between the bitcoin full node and the Utreexo node.
+When the block broadcasts from the Utreexo node to the full node, the proof is stripped away, on the other hand, the proof is placed.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+The paper also mentions that, analyzing the historical record of bitcoin
+About 40\% of UTXO will be consumed in 20 blocks.
+Nearly 80\% of UTXO will be consumed in 1000 blocks.
+So by using a small amount of memory space to cache the most recent UTXO, you can skip transmitting many proofs.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+The difference from this study is that this study considers account-based cryptocurrencies, rather than UTXO-based ones.
+At the same time, this study additionally considers the situation when bifurcation occurs.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\subsection{Making Data Structure Persistent}
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+The paper~\cite{b2} proposes a variety of algorithms that enable any node-based data structure to be partial/fully persistent.
+According to the node-splitting algorithm of that paper, it is even possible to complete the insertion and modification of a doubly linked list within the $O(1)$ time complexity.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+However, the paper does not propose a way to remove older versions of the persistent data structure.
+This makes it difficult to apply these algorithms to the caching of shallow state blockchains.
+Because the inability to delete past versions will result in the space needed for caching never being released.
 
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{b1} Dryja, Thaddeus. Utreexo: A dynamic hash-based accumulator optimized for the Bitcoin UTXO set. Vol. 2019. IACR Cryptology ePrint Archive, 2019.
+\bibitem{b2} Driscoll, James R., et al. "Making data structures persistent." Proceedings of the eighteenth annual ACM symposium on Theory of computing. 1986.
 \end{thebibliography}

### 2020-05-15 ctapc/paper.tex
完成 ctapc

@@
 
-\title{The Design of Shallow State Blockchain*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{The Design of Shallow State Blockchain}
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\author{\IEEEauthorblockN{1\textsuperscript{st} TSAI, TSUEN-JE}
+\IEEEauthorblockA{\textit{Department of Computer Science \& Information Engineering} \\
+\textit{National Taiwan University}\\
+Taipei, Taiwan \\
+r05922086@ntu.edu.tw}
 }
@@
 \section{Introduction}
-In 2008, Satoshi Nakamoto proposed the white paper of bitcoin.
+In 2008, Satoshi Nakamoto proposed the white paper of bitcoin~\cite{b3}.
 It is a new type of cryptocurrency system based on blockchain.
@@
 However, as the data size of ledger got bigger and bigger, storage space of node increased yearly.
-Ten years later, it costs hundreds of GB storage space for a node to run some well-known cryptocurrency system, such as Bitcoin and Ethereum.
+Ten years later, it costs hundreds of GB storage space for a node to run some well-known cryptocurrency system, such as Bitcoin and Ethereum~\cite{b4}.
 Thus, it gradually make the nodes maintained by person overload.
@@
 Extended by this idea, if we cache the accounts’ information appearing in recent transactions, there is no need to verify the proof again when the accounts make transactions.
+
 To go a step further, if nodes on the Internet follow the same set of rules to record cache, it will reach a consensus that node knows whether to attach the proof.
@@
 \subsection{cache design}
-The problems mentioned above can be avoided by a simple design principle.
+We can make every node's cache the same by a simple design principle.
 Namely, each block has its own cache, and the content of cache depends on which chain the block is situated.
@@
 \subsection{persistent cache}
-In this part, we take another approach: every block retains its own cache.
+We take an approach: every block retains its own cache.
 When a new block is about to append to the chain, it can directly use the cache of the previous block.
@@
 If a cache is full, it will discard a piece of data before inserting new data.
-The least recently used data are chosen by LRU strategy, and it will be discarded.
+In LRU strategy, the least recently used data will be discarded.
 The reasons why LRU has higher hit rate than FIFO are revealed by the history data of Ethereum.
-First, after an account spends money, it is highly possible that it will spend money again.
-Second, after an account receives money,  it is highly possible that it will spend money right away.
-Because LRU updates the using time of data, it is able to keep caching the data appearing frequently.
+First, after an account spends money,
+it is highly possible that it will spend money again.
+Second, after an account receives money,
+it is highly possible that it will spend money right away.
+Because LRU updates the using time of data,
+it is able to keep caching the data appearing frequently.
 However, FIFO only looks at the coming time of data.
-Even if some data appear frequently, they will be discarded sooner or later.
+Even if some data appear frequently,
+they will be discarded sooner or later.
+
 From an abstract view, LRU is a data structure that supports two kinds of interface.
@@
 There is one simple idea that we directly combine persistent-versioned alternatives of a hash table and a doubly linked list, and then we get a persistent LRU.
-Although there are mature alternatives for hash tables, it is hard to find such a thing for doubly linked lists.
+Although there are mature alternatives~\cite{b5}~\cite{b6} for hash tables, it is hard to find such a thing for doubly linked lists.
 Thus, we need to use other persistent and efficient data structures to replace doubly linked lists. The things that an abstract doubly linked list can do are as follows.
@@
 \end{itemize}
-Following we will discuss how to use red-black tree to complete the above tasks and introduce our design of order tree, which is more efficient than red-black tree.
+Following we will discuss how to use red-black tree~\cite{b7} to complete the above tasks and introduce our design of order tree, which is more efficient than red-black tree.
 
@@
 it could be $block\_height * max\_tx\_in\_one\_block+ tx\_number$.
+
 Afterwards, build a red-black tree whose key is timestamp and value is account’s information. About hash table, the account's address is set as key and the correspondent timestamp is set as value.
 While executing get, it first gets the timestamp from the account's address in the hash table, and then gets the account’s information from the timestamp in the red-black tree.
-For example, in Fig 3.6, we first get the account’s timestamp, 243, from the hash table, and search 243 in red-black tree.
+For example, in Fig 1, we first get the account’s timestamp, 243, from the hash table, and search 243 in red-black tree.
 After searching, it needs to update the using time.
@@
 However, it needs to modify the account's information.
-Fig 3.6 shows the sharing structure of the persistent red-black tree.
+Fig 2 shows the sharing structure of the persistent red-black tree.
 In this figure, the cache size is 8.
@@
 Therefore, it has to delete the data of minimum timestamp; that is, the red 7 at lower left corner will be deleted.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{../images/ht-rb-tree}
+  \caption{hash table + red-black tree}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{../images/immutable-rb-tree}
+  \caption{immutable red-black tree}
+\end{figure}
+
+\subsection{hash table + order tree}
+Doubly linked list records order relations by the pointer relations of nodes.
+Red-black tree has to additionally record the timestamp.
+Moreover, the account’s information that we can search with the hash table in one time now needs two steps with red-black tree; namely, we find the timestamp from the address, and then find the account's information from the timestamp.
+The reason why doubly linked lists cannot turn into persistent data structure through path copying is that two adjacent nodes always point to each other.
+Once modifying the node by path copying, it has to copy the whole list.
+Therefore, we want to find another way to connect the nodes.
+
+Image to weave a net behind the nodes, and then stick them together.
+The basic form of the net structure is a full binary tree. We name the structure using a full binary tree to store order data as order tree. We will introduce the operations of order tree as follows.
+
+If cache size is n, the height of the order tree will be set as 1 + logn.
+That is to say, the number of leaves is at least two times the cache size.
+Fig.
+3 shows that there is an order tree with size 4, and it has 8 leaf nodes.
+
+Applying to LRU cache, the value stored by the hash table is a pointer pointing to the leaf node of the order tree. It only needs one time to get the data by searching the hash table. 
+Order tree stores the entire data in leaf nodes, and each data is arranged in the order of time.
+In this paper, the newer the data, the more the right side of the leaf position.
+We will explain and draw in this way.
+
+Some leaf nodes in the order tree have stored data, while some of them haven’t. We call the leaf with data as “used leaf”, and the leaf without data as “unused leaf”.
+While executing get, change the used leaf into an unused leaf if it has been searched, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf.
+While executing put, first find the leftmost used leaf and change it into unused, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf.
+No matter get or put, it always occupies a leaf on the right.
+If the used leaf is on the rightmost of the tree, it has to execute full copy.
+Therefore, make all the used leaves tightly packed together to the left side of the new order tree in the original order.
+
+Fig.
+4 shows a series of execution of order tree.
+In this figure, full copy happens at the time when state 7 turns into state 8.
+The light blue nodes in the figure mean that they are unused.
+Notice that we painted all unused leaves of subtree light blue.
+In implementation, there is no need to allocate memory space to light blue nodes. The pointer pointing to light blue subtree is a null pointer.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{../images/order-tree}
+  \caption{order tree with size 4}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{../images/order-trees}
+  \caption{order tree multiple operation}
+\end{figure}
+
+\subsubsection{complexity analysis}
+In the following analysis, the size of the order tree is $n$.
+If full copy doesn’t happen, execution of get and put go through root to leaf two times.
+The height of the order tree is $O(\log n)$, and the time and space complexity are both $O(\log n)$.
+
+If full copy happens, it has to go through the order tree,
+and has all used leaves congregate to form a new tree.
+Notice that the total number of nodes of a full binary tree is two times the quantity of leaves minus one,
+and the total number won’t exceed $8*n$.
+Therefore, the time and space complexity are both $O(n)$.
+
+It may be a little high for the $O(n)$ complexity.
+However, everytime when operating get or put only
+make the used leaf move one grid to the right.
+It costs  at least n operations for the used leaf
+to go to the rightmost of the tree. Thus, if the
+cost of full copy is amortized to every operation,
+the time and space complexity are both $O(1)$,
+and time and space complexity of get and put are still $O(\log n)$.
 
@@
 
+\section{Conclusion}
+This paper describes the design of shallow state blockchain and discusses the advantages and disadvantages of multiple cache strategies.
+Especially for the LRU cache strategy, 
+we first try the combination of persistent hash table and persistent red-black trees,
+Further proposed a novel data structure, order tree, let it be combined with persistent hash,
+Get a more efficient implementation of persistent LRU.
+
 \begin{thebibliography}{00}
@@
 \bibitem{b2} Driscoll, James R., et al. "Making data structures persistent." Proceedings of the eighteenth annual ACM symposium on Theory of computing. 1986.
+\bibitem{b3} Nakamoto, Satoshi. Bitcoin: A peer-to-peer electronic cash system. Manubot, 2019.
+\bibitem{b4} Wood, Gavin. "Ethereum: A secure decentralised generalised transaction ledger." Ethereum project yellow paper 151.2014 (2014): 1-32.
+\bibitem{b5} BAGWELL, Phil. Ideal hash trees. 2001.
+\bibitem{b6} Stucki, Nicolas, et al. "RRB vector: a practical general purpose immutable sequence." Proceedings of the 20th ACM SIGPLAN International Conference on Functional Programming. 2015.
+\bibitem{b7} Guibas, Leo J., and Robert Sedgewick. "A dichromatic framework for balanced trees." 19th Annual Symposium on Foundations of Computer Science (sfcs 1978). IEEE, 1978.
 \end{thebibliography}
 \vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2020-05-15 abstract.tex
修正章節概述

@@
 \bigbreak
-\noindent \textbf{關鍵字：區塊鏈、無狀態區塊鏈、快取、資料結構}{\, \makeatletter \@keywordszh \makeatother}
+\noindent
+關鍵字：區塊鏈、無狀態區塊鏈、快取、資料結構
 \end{abstractzh}
@@
 \bigbreak
-\noindent \textbf{Keywords:blockchain, stateless blockchain, cache, data structure}{\, \makeatletter \@keywordsen \makeatother}
+\noindent
+Keywords: blockchain, stateless blockchain, cache, data structure
 \end{abstracten}
 
-\begin{comment}
-\category{I2.10}{Computing Methodologies}{Artificial Intelligence --
-Vision and Scene Understanding} \category{H5.3}{Information
-Systems}{Information Interfaces and Presentation (HCI) -- Web-based
-Interaction.}
+% \begin{comment}
+% \category{I2.10}{Computing Methodologies}{Artificial Intelligence --
+% Vision and Scene Understanding} \category{H5.3}{Information
+% Systems}{Information Interfaces and Presentation (HCI) -- Web-based
+% Interaction.}
 
-\terms{Design, Human factors, Performance.}
+% \terms{Design, Human factors, Performance.}
 
-\keywords{Region of interest, Visual attention model, Web-based
-games, Benchmarks.}
-\end{comment}
+% \keywords{Region of interest, Visual attention model, Web-based
+% games, Benchmarks.}
+% \end{comment}

### 2020-05-15 ctapc/paper.tex
修正章節概述

@@
 \section{Introduction}
-In 2008, Satoshi Nakamoto proposed the white paper of bitcoin~\cite{b3}.
-It is a new type of cryptocurrency system based on blockchain.
-In this system, each node maintain a complete ledger in order to attain the high degree of decentralization of entire system.
-However, as the data size of ledger got bigger and bigger, storage space of node increased yearly.
-Ten years later, it costs hundreds of GB storage space for a node to run some well-known cryptocurrency system, such as Bitcoin and Ethereum~\cite{b4}.
-Thus, it gradually make the nodes maintained by person overload.
-If we settle for second best by saving the information needed for verifying new block, such as UTXO in Bitcoin and world state in Ethereum, it still needs several or tens of GB for disk storage place.
-With this method, not only the storage space of disk is requested but also  I/O speed.
-Furthermore, it is too slow for traditional disk to access randomly.
-The speed of verifying a block on Ethereum can't keep up with the generation speed of blocks.
-It force the node maintainer on Ethereum to buy expensive solid-state disk, and it further cause the increase in operation cost of node.
+In 2008, Satoshi Nakamoto proposed the white paper
+of bitcoin~\cite{b3}. It is a new type of cryptocurrency
+system based on blockchain. In this system, each node
+maintain a complete ledger in order to attain the
+high degree of decentralization of entire system.
+However, as the data size of ledger got bigger and bigger,
+storage space of node increased yearly. Ten years later,
+it costs hundreds of GB storage space for a node to run
+some well-known cryptocurrency system, such as Bitcoin and
+Ethereum~\cite{b4}. Thus, it gradually make the nodes maintained
+by person overload. If we settle for second best by saving the
+information needed for verifying new block, such as UTXO in
+Bitcoin and world state in Ethereum, it still needs
+several or tens of GB for disk storage place. With
+this method, not only the storage space of disk is
+requested but also  I/O speed. Furthermore, it is
+too slow for traditional disk to access randomly.
+The speed of verifying a block on Ethereum can't keep
+up with the generation speed of blocks. It force the node
+maintainer on Ethereum to buy expensive solid-state disk,
+and it further cause the increase in operation cost of node.
 
-To deal with the problem above, cryptocurrency communities start trying several solutions, and stateless blockchain is prospective one of them.
-It only need to store block header for each node on stateless blockchain.
-Nevertheless, each transaction must be attached with proof of validity.
-This approach significantly reduces the requirement of storage space.
-Furthermore, it is no need to search the validity of transaction on disk; namely, it drastically reduces the I/O time.
+To deal with the problem above, cryptocurrency communities
+start trying several solutions, and stateless blockchain
+is prospective one of them. It only need to store
+block header for each node on stateless blockchain.
+Nevertheless, each transaction must be attached with
+proof of validity. This approach significantly reduces
+the requirement of storage space. Furthermore, it is
+no need to search the validity of transaction on disk;
+namely, it drastically reduces the I/O time.
 
 This paper proposes an imrpovement to stateless blockchain.
-We let the node on stateless blockchain reach a consensus to maintain a cache.
-If the payer of transaction appears in recent transaction, it is highly possible to infer the validity from cache.
-Hence, due to the omission of proof of validity, it reduces the size of transaction and the Internet traffic while broadcasting.
-However, how to maintain cache effectively becomes a new problem.
-When a new block append to the blockchain, there will be a correspondent cache.
-Nevertheless, there will also exist overlap on the blocks nearby.
-Therefore, we design persisted data structure for different cache strategies, such as the nearest k blocks and LRU, and we conduct an experiment to test their performance.
+We let the node on stateless blockchain reach a consensus
+to maintain a cache. If the payer of transaction appears
+in recent transaction, it is highly possible to infer
+the validity from cache. Hence, due to the omission of
+proof of validity, it reduces the size of transaction and
+the Internet traffic while broadcasting. However, how
+to maintain cache effectively becomes a new problem.
+When a new block append to the blockchain, there will be
+a correspondent cache. Nevertheless, there will
+also exist overlap on the blocks nearby.
+Therefore, we design persisted data structure
+for different cache strategies, such as the
+nearest k blocks and LRU, and we conduct an
+experiment to test their performance.
 
 The remaining sections are arranged as follows.
-Section II narratives some related works, whereas section III describes the background of this paper and preliminary knowledge; section IV illuminates the design of stateless blockchain, including cache strategies and data structures used by cache; section V shows the design and results of experiment; section VI discusses future extensions to stateless blockchain, and concluding remarks are found in section VII.
+section II illuminates the design of stateless blockchain,
+including cache strategies and data structures
+used by cache; Section III narratives some related works,
+and concluding remarks are found in section IV.
 

### 2020-05-23 abstract.tex
中文術語修正、補上部分術語的英文

@@
 \begin{abstractzh}
-基於區塊鏈的虛擬貨幣是一種點對點的交易系統，
+基於區塊鏈的加密貨幣是一種點對點的交易系統，
 在此去中心化的系統中，

### 2020-06-14 abstract.tex
減少「硬碟」術語的使用
ctapc加上實驗

@@
 \begin{abstractzh}
-基於區塊鏈的加密貨幣是一種點對點的交易系統，
-在此去中心化的系統中，
+基於區塊鏈的加密貨幣網路中，
 每個節點都維護一個完整的賬本，
-其中記錄了所有賬戶的全部交易資料。
-這樣的系統具有不容易被竄改資料的特點，
-然而此種特性會使得所需要儲存的資料只增不減，
-經年累月下來，對單個節點的儲存容量要求只會越來越高，
-一旦個體維護的節點逐漸不勘負荷，
-將導致此區塊鏈的中心化程度逐步上升。
-
+經年累月，賬本的儲存容量越來越高，
+維護一個節點的成本也會越來越高。
 無狀態區塊鏈是一種針對以上問題的改進方案，
 它的每一筆交易中附上了合法性證明，
-使得節點不需要進入硬碟查找過往賬本資訊，
+使得節點不需要進入資料儲存裝置查找過往賬本資訊，
 只要驗證交易內附的證明即可，
-從而使節點所需儲存資訊大幅減少。
+從而使節點所需儲存的資訊量大幅減少，
+然而，要付出額外的網路流量與驗證時間。
 
-在本論文中，我們將討論以下兩點：
-第一，並無必要在每一筆交易都附上證明，
-只要快取部分訊息，
-一筆交易的合法性很可能由最近出現過的其他交易的合法性推知。
-第二，當區塊鏈發生分叉時，必須回到分叉點再產生新區塊的快取，
-為此我們設計了不可變的資料結構，
-使得快取能夠在各種情況下被快速計算。
-最後，進行實驗來瞭解數種快取策略與資料結構在不同工作量（workload）下的表現。
+在本論文中，我們將在基於帳號的區塊鏈上討論以下兩點：
+第一，
+一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
+只要快取帳號的訊息，
+就可以省略部分交易的證明，
+以此來減少網路流量與驗證時間。
+第二，
+快取替換有多種策略，針對 LRU 策略，
+設計了基於不可變紅黑樹與不可變順序樹的兩種資料結構，
+並且進行實驗比較了快取命中與快取失效的代價，
+模擬現今以太坊的區塊性質，
+當快取數十個區塊大小的賬戶資訊量時，
+快取命中所需的查找時間仍數倍低於梅克爾 Patricia 證明驗證的時間。
 
@@
 
-Cryptocurrency based on blockchain is a peer to peer trading system.
-In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account.
-The system has the characteristics that it is very hard to tamper with the data.
-However, such characteristic only makes the data increase but do not decrease.
-Years after years, requirement to single node will get higher and higher.
-Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise.
+Cryptocurrency based on blockchain is a peer to peer trading
+system. In this decentralized system,
+each node maintain a complete ledger which
+records entire transaction history of all account.
+Years after years, requirement to single node will
+get higher and higher. Dealing with the issue, stateless
+blockchain is a promising approach. To be more specific,
+in this system, each transaction is attached with proof
+of validity. With this approach, there is no need for a node
+to access the data storage device to search past information
+of the ledger. Instead, node only verifies the proof attached
+to each transaction. Therefore, it will significantly
+reduce the space of data storage for each node.
+But it will cause additional network traffic and
+verification time.
 
-Dealing with the issue, stateless blockchain is a promising approach.
-To be more specific, in this system, each transaction is attached with proof of validity.
-With this approach, there is no need for a node to access the disk to search past information of the ledger.
-Instead, node only verifies the proof attached to each transaction.
-Therefore, it will significantly reduce the space of data storage for each node.
-
-In this paper, we will discuss the following two points.
-First, it only need to cache part of information instead of attaching proof to each transaction.
-It is highly possible to infer the validity of a transaction from other valid transaction appearing recently.
-Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks.
-To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation.
-Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures.
+In this paper, we will discuss the following two points
+on the account-based.
+First,
+It is highly possible to infer the validity of
+a transaction from other valid transaction appearing recently.
+If we cache account information, we can eliminate some
+proof in transactions and then reduce network traffic
+and verification time.
+Second,
+There are so many cache replacement polices.
+For LRU polices, we designed two composite data
+structures which based on red-black tree and order tree.
+And conduct some experiments to compare the costs of
+cache hit with the penalty of cache miss.
+Simulating today's Ethereum's block property,
+when cache size can contain several tens of blocks' information,
+the cache searching time is significantly lower than
+the time to verify Merkle Patricia proofs.
 

### 2020-06-14 ctapc/paper.tex
ctapc加上實驗

@@
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+% \usepackage{algorithmic}
 \usepackage{graphicx}
@@
 \usepackage{xcolor}
+\usepackage{hyperref}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{abstract}
-Cryptocurrency based on blockchain is a peer to peer trading system.
-In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account.
-The system has the characteristics that it is very hard to tamper with the data.
-However, such characteristic only makes the data increase but do not decrease.
-Years after years, requirement to single node will get higher and higher.
-Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise
+Cryptocurrency based on blockchain is a peer to peer trading
+system. In this decentralized system,
+each node maintain a complete ledger which
+records entire transaction history of all account.
+Years after years, requirement to single node will
+get higher and higher. Dealing with the issue, stateless
+blockchain is a promising approach. To be more specific,
+in this system, each transaction is attached with proof
+of validity. With this approach, there is no need for a node
+to access the data storage device to search past information
+of the ledger. Instead, node only verifies the proof attached
+to each transaction. Therefore, it will significantly
+reduce the space of data storage for each node.
+But it will cause additional network traffic and
+verification time.
 
-Dealing with the issue, stateless blockchain is a promising approach.
-To be more specific, in this system, each transaction is attached with proof of validity.
-With this approach, there is no need for a node to access the disk to search past information of the ledger.
-Instead, node only verifies the proof attached to each transaction.
-Therefore, it will significantly reduce the space of data storage for each node.
-
-In this paper, we will discuss the following two points.
-First, it only need to cache part of information instead of attaching proof to each transaction.
-It is highly possible to infer the validity of a transaction from other valid transaction appearing recently.
-Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks.
-To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation.
-Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures
+In this paper, we will discuss the following two points
+on the account-based.
+First,
+It is highly possible to infer the validity of
+a transaction from other valid transaction appearing recently.
+If we cache account information, we can eliminate some
+proof in transactions and then reduce network traffic
+and verification time.
+Second,
+There are so many cache replacement polices.
+For LRU polices, we designed two composite data
+structures which based on red-black tree and order tree.
+And conduct some experiments to compare the costs of
+cache hit with the penalty of cache miss.
+Simulating today's Ethereum's block property,
+when cache size can contain several tens of blocks' information,
+the cache searching time is significantly lower than
+the time to verify Merkle Patricia proofs.
 \end{abstract}
@@
 
-This paper proposes an imrpovement to stateless blockchain.
+This paper proposes an improvement to stateless blockchain.
 We let the node on stateless blockchain reach a consensus
@@
 The using time of the new key-value pair should be the latest.
-Corresponding to the situation of stateless blockchain, everytime when a new block appends to the chain, we have to compute the cache of the new block.
+Corresponding to the situation of stateless blockchain, every time when a new block appends to the chain, we have to compute the cache of the new block.
 In this time, a series of read and modify execution of accounts will turn into get and put.
@@
 
-If cache size is n, the height of the order tree will be set as 1 + logn.
+If cache size is n, the height of the order tree will be set as 1 + log n.
 That is to say, the number of leaves is at least two times the cache size.
@@
 4 shows a series of execution of order tree.
-In this figure, full copy happens at the time when state 7 turns into state 8.
+In this figure, full copy happens at the time when state 6 turns into state 7.
 The light blue nodes in the figure mean that they are unused.
@@
 and time and space complexity of get and put are still $O(\log n)$.
+
+\section{experiment}
+In this section, we evaluated the performances of 
+persistent LRU implemented in different data 
+structures under different workload.
+
+\subsection{Experiment Environment}
+All experiments were all conducted on the workstation below:
+
+\begin{itemize}
+\item CPU: AMD Ryzen 7 2700X (8 cores 16 threads, 3.6 GHz, 32K L1d cache, 64k L1i cache, 512K L2 cache、8M L3 cache)
+\item memory: DDR4 64 GB
+\item OS: Linux manjaro 4.19.36-1-MANJARO x86\_64
+\item compiler: GCC 9.1.0
+\end{itemize}
+
+\subsection{Data Structures}
+
+We use C++ 17 implemented three data structures:
+
+\begin{itemize}
+\item hash table + doubly-linked list, it will copy itself when creating a new version
+\item persistent hash table + persistent red-black tree
+\item persistent hash table + persistent order tree
+\end{itemize}
+
+Because what we want to simulate is blockchain,
+all workload use block as unit.
+There are many get/put instructions in a block.
+To optimize this kind of workload,
+the persistent data structures described above all
+support transience. That means data structure doesn't 
+generate a new version for every get/put instruction,
+but generate an temporary ephemeral data structures and
+make it immutable one after operating batch of instructions.
+While eliminating lots of intermediate states,
+this optimization can significantly improve performance.
+
+We claim that, in our implementation:
+Hash table is unordered\_map in C++ standard library.
+For persistent hash table, we use famous C++
+persistent data structures library \href{https://sinusoid.es/immer/}{immer}.
+Doubly-linked list, persistent red-black tree,
+persistent order tree are all implemented by ourselves.
+
+From now on, we will refer to these three composite data structures
+as doubly linked list, red-black tree, and order tree.
+
+\subsection{performance}
+
+\subsubsection{workload}
+We use a simple model to simulate block generation,
+there are n nodes in the network,
+Each node will mine for the highest block
+(that is, the top of the longest chain it recognizes).
+Initially, The highest block of each node
+is genesis block. Afterwards, there were several rounds,
+In each round, each node has a certain probability
+to dig out new blocks. If it is not dug,
+It will go to the successor block of the
+highest block dug by other nodes,
+if the highest block does not have any successor block,
+node will randomly go to other longest chains.
+If no node has dug out any block,
+the same process will be repeated.
+
+In all workloads, it is assumed that there
+are 10 nodes in the network, and the probability
+of each node to dig out new block in one round is one-tenth.
+The block generating process will stop after mining 1000 blocks.
+Under this setting, there will be about
+1.5 blocks at the same height.
+
+From \href{https://etherscan.io/chart/gaslimit}{etherscan}, we can
+know that Ethereum's gas limit is about ten million, and
+it will cost 21000 gas fee per transaction.
+After simple division, a block can contain about 500 transactions.
+Therefore, the number of get/put instructions
+for one block of our workload is set to 500.
+
+In addition, There is another argument, get/put rate.
+For normal ethereum transaction,
+payment always results in state changing,
+but it's not true when smart contract is involved.
+Therefore, it is possible get/put instructions both appear.
+If there is no additional explanation below,
+the put instruction will account for 50 \% (get instruction also accounts for 50 \%).
+
+Before starting any task, we will first fill
+the entire cache, if not, when the cache size is set too large,
+workload takes a long time to fill it up,
+and the state when the cache is not full is not our concern,
+as the blockchain is usually composed of millions of blocks,
+For most of the time, the cache is full.
+
+\subsubsection{Adjust Cache Size}
+
+The first experiment fix hit rate to 100\%,
+and adjust the size of cache (the number of key-value pairs).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{adjust_cache_size.png}
+  \caption{adjust cache size}
+\end{figure}
+
+In Fig. 5, we can see that time cost by doubly-linked list
+is proportional to the cache size. It's because that
+the main cost of doubly-linked list is on replication.
+How big is the cache, how much is the amount to be copied each time the block is updated
+
+The growth curve of the red-black tree and the sequence
+tree is rather gentle ($O(\log n)$).
+Noting that the line graph of the order tree,
+compared to the smooth growth of the red-black tree,
+is somewhat oscillating,
+Because the number of leaves of the
+order tree is $1 + \lceil \log_2 n \rceil$,
+its number of leaves is more discrete,
+When the cache size reaches the power of $2^k$,
+the number of leaves doubles, which will affect
+the performance and cause oscillating.
+
+\subsubsection{Adjust hit rate}
+
+In this experiment, we fix cache size to 30000, and adjust hit rate.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{adjust_hit_rate.png}
+  \caption{adjust hit rate}
+\end{figure}
+
+In Fig 6, we can see that the hit rate has no effect
+on the doubly linked list, because its main consumption
+comes from replication, the only thing to do
+after the cache hit is to move a few pointer,
+it doesn't take much time.
+The time consumption of red-black trees and order
+trees will increase with the increase of hit rate.
+Because their main time-consuming comes from path copying,
+the more cache hits, the more branches need
+to be copied and created.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{adjust_put_rate.png}
+  \caption{adjust put rate}
+\end{figure}
+
+Set the cache size to 30000, the hit rate to 1.0,
+and adjust the proportion of put in the get/put instructions.
+It can be seen from Figure 7 that the performance
+is basically not affected.
+
+\subsection{Miss Penalty}
+
+When verifying a transaction whose related account information
+is not in the cache of the node (cache miss),
+This transaction must be accompanied by a proof
+for verification. Therefore, There are two penalties when cache miss:
+(1) It cost network I/O to receive the proof, which is directly related
+to the size of the proofs.
+(2) The CPU execution time consumed by the proof verification.
+
+From Fig 7 we can know that, when cache size is 30000,
+put rate is 100\%, hit rate is 1.0, order tree implementation
+can process 1000 blocks in 1.241 seconds, that means 
+the average time to process a block is 1.241 milliseconds.
+This number will be smaller when the cache size is smaller.
+
+We chose Merkle Patricia tree verification cost to compare
+with the order tree implementation,
+We choose \href{https://docs.rs/trie-db/0.20.1/trie_db/index.html}{trie-db} module,
+which is the part of one of the two major
+Ethereum implementations,
+\href{https://www.parity.io/ethereum/}{Parity Ethereum}, to conduct experiment.
+
+There are two factors that influence
+Merkle Patricia proof's verification performance:
+(1) If the number of leaves is $s$,
+the size of the proof is about $O(\log s)$.
+The time complexity of verifying a proof is also $O(\log s)$.
+(2) The number of proof in one batch.
+A Merkle proof is a branch of the Merkle tree.
+When a node is shared by multiple branches,
+there is no need to repeat calculations.
+So the time to verify $k$ proofs at a time will be
+shorter than $k$ times the time to verify a proof.
+
+By the information of \href{https://www.etherchain.org/charts/totalAccounts}{etherchain.org},
+the number of Ethereum accounts today has exceeded 80 million,
+So we first randomly insert 80 million pieces
+of data into the Merkle Patricia
+tree (that is, the number of leaves is 80 million),
+And based on the assumption of 500 transactions in
+one block, we batch verify 500 proofs at a time,
+The measured time is 5.536 milliseconds, which is
+obviously more time-consuming than direct access to cache.
+
+In the aspect of I/O overhead, the proof size of a
+block is about 900 KB, and 1000 blocks is almost 900 MB.
+If we use the common home network today,
+the time required to download these additional
+proof is more time-consuming than verifying the proofs.
+
+\subsection{Experiment Conclusion}
+
+The Experiments verify that order tree and red-black tree
+have lower time complexity. When the cache size increases
+to a certain extent, they significantly beat ever-copy
+doubly linked list in performance. Compared with
+red-black tree, order tree does not need to maintain
+the color of the node, and to execute various rotation rules,
+There is a little advantage in execution speed.
+
+At the same time, we also experimented and measured
+the proof size and verification speed of the Merkle
+Patricia tree. Understand that under normal circumstances,
+reading the cache directly is faster than downloading
+and verifying the proof. Based on these data,
+it can be deduced that if Merkle Patricia tree
+is used as vector commitment, if the shallow state
+blockchain adopts an appropriate cache size, it
+can bring speed improvement under the LRU strategy.
 

### 2020-06-15 abstract.tex
調整格式以通過 ieee blockchain 的檢測

@@
 system. In this decentralized system,
-each node maintain a complete ledger which
-records entire transaction history of all account.
+each node maintains a complete ledger which
+records entire transaction history of all accounts.
 Years after years, requirement to single node will
@@
 In this paper, we will discuss the following two points
-on the account-based.
+on account-based blockchain.
 First,
 It is highly possible to infer the validity of
-a transaction from other valid transaction appearing recently.
+a transaction from another valid transaction appearing recently.
 If we cache account information, we can eliminate some

### 2020-06-15 ctapc/paper.tex
調整格式以通過 ieee blockchain 的檢測

@@
 \usepackage{xcolor}
-\usepackage{hyperref}
+
+\columnsep 0.24in
+\addtolength{\topmargin}{0.075in}
+\addtolength{\textheight}{-0.1in}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{The Design of Shallow State Blockchain}
+\title{Structural Assessment on Stateless Blockchain Improvements with
+LRU-oriented Cache Replacement Policy}
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} TSAI, TSUEN-JE}
-\IEEEauthorblockA{\textit{Department of Computer Science \& Information Engineering} \\
-\textit{National Taiwan University}\\
-Taipei, Taiwan \\
-r05922086@ntu.edu.tw}
-}
+% \author{\IEEEauthorblockN{1\textsuperscript{st} TSAI, TSUEN-JE}
+% \IEEEauthorblockA{\textit{Department of Computer Science \& Information Engineering} \\
+% \textit{National Taiwan University}\\
+% Taipei, Taiwan \\
+% r05922086@ntu.edu.tw}
+% }
 
@@
 including cache strategies and data structures
-used by cache; Section III narratives some related works,
-and concluding remarks are found in section IV.
+used by cache; Section III show the design and
+results of experiments; Section IV narratives some related works,
+and concluding remarks are found in section V.
 
@@
 \begin{itemize}
-\item CPU: AMD Ryzen 7 2700X (8 cores 16 threads, 3.6 GHz, 32K L1d cache, 64k L1i cache, 512K L2 cache、8M L3 cache)
+\item CPU: AMD Ryzen 7 2700X (8 cores 16 threads, 3.6 GHz, 32K L1d cache, 64k L1i cache, 512K L2 cache, 8M L3 cache)
 \item memory: DDR4 64 GB
@@
 For persistent hash table, we use famous C++
-persistent data structures library \href{https://sinusoid.es/immer/}{immer}.
+persistent data structures library immer.
 Doubly-linked list, persistent red-black tree,
@@
 
-From \href{https://etherscan.io/chart/gaslimit}{etherscan}, we can
+From etherscan, we can
 know that Ethereum's gas limit is about ten million, and
@@
 with the order tree implementation,
-We choose \href{https://docs.rs/trie-db/0.20.1/trie_db/index.html}{trie-db} module,
-which is the part of one of the two major
+We choose trie-db module,
+which is a part of one of the two major
 Ethereum implementations,
-\href{https://www.parity.io/ethereum/}{Parity Ethereum}, to conduct experiment.
+Parity Ethereum, to conduct experiment.
 
@@
 
-By the information of \href{https://www.etherchain.org/charts/totalAccounts}{etherchain.org},
+By the information of etherchain.org,
 the number of Ethereum accounts today has exceeded 80 million,

### 2020-06-22 abstract.tex
修正 6/22 會議後文法與用字問題

@@
 
-在本論文中，我們將在基於帳號的區塊鏈上討論以下兩點：
+在本論文中，我們將在基於賬號的區塊鏈上討論以下兩點：
 第一，
 一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
-只要快取帳號的訊息，
+只要快取賬號的訊息，
 就可以省略部分交易的證明，
@@
 快取替換有多種策略，針對 LRU 策略，
-設計了基於不可變紅黑樹與不可變順序樹的兩種資料結構，
+設計了基於不可變紅黑樹與不可變值無關順序樹的兩種資料結構，
 並且進行實驗比較了快取命中與快取失效的代價，
@@
 First,
-It is highly possible to infer the validity of
+it is highly possible to infer the validity of
 a transaction from another valid transaction appearing recently.
@@
 Second,
-There are so many cache replacement polices.
+there are so many cache replacement polcies.
 For LRU polices, we designed two composite data
-structures which based on red-black tree and order tree.
-And conduct some experiments to compare the costs of
-cache hit with the penalty of cache miss.
+structures which based on red-black tree and value-independent order tree.
+And conduct some experiments to compare the cost of a
+cache hit with the penalty of a cache miss.
 Simulating today's Ethereum's block property,

### 2020-06-22 ctapc/paper.tex
修正 6/22 會議後文法與用字問題

@@
 Second,
-There are so many cache replacement polices.
-For LRU polices, we designed two composite data
-structures which based on red-black tree and order tree.
+There are so many cache replacement policies.
+For LRU policies, we designed two composite data
+structures which based on red-black tree and value-independent order tree.
 And conduct some experiments to compare the costs of
@@
 \end{itemize}
-Following we will discuss how to use red-black tree~\cite{b7} to complete the above tasks and introduce our design of order tree, which is more efficient than red-black tree.
+Following we will discuss how to use red-black tree~\cite{b7} to complete the above tasks and introduce our design of value-independent order tree, which is more efficient than red-black tree.
 
@@
 
-\subsection{hash table + order tree}
+\subsection{hash table + value-independent order tree}
 Doubly linked list records order relations by the pointer relations of nodes.
@@
 Image to weave a net behind the nodes, and then stick them together.
-The basic form of the net structure is a full binary tree. We name the structure using a full binary tree to store order data as order tree. We will introduce the operations of order tree as follows.
+The basic form of the net structure is a full binary tree.
+We name the structure using a full binary tree to store order data as value-independent order tree.
+We will introduce the operations of value-independent order tree as follows.
 
-If cache size is n, the height of the order tree will be set as 1 + log n.
+If cache size is n, the height of the value-independent order tree will be set as 1 + log n.
 That is to say, the number of leaves is at least two times the cache size.
 Fig.
-3 shows that there is an order tree with size 4, and it has 8 leaf nodes.
+3 shows that there is an value-independent order tree with size 4, and it has 8 leaf nodes.
 
-Applying to LRU cache, the value stored by the hash table is a pointer pointing to the leaf node of the order tree. It only needs one time to get the data by searching the hash table. 
-Order tree stores the entire data in leaf nodes, and each data is arranged in the order of time.
+Applying to LRU cache, the value stored by the hash table is a pointer pointing to the leaf node of the value-independent order tree.
+It only needs one time to get the data by searching the hash table.
+value-independent order tree stores the entire data in leaf nodes, and each data is arranged in the order of time.
 In this paper, the newer the data, the more the right side of the leaf position.
@@
 
-Some leaf nodes in the order tree have stored data, while some of them haven’t. We call the leaf with data as “used leaf”, and the leaf without data as “unused leaf”.
+Some leaf nodes in the value-independent order tree have stored data, while some of them haven’t. We call the leaf with data as “used leaf”, and the leaf without data as “unused leaf”.
 While executing get, change the used leaf into an unused leaf if it has been searched, and then write the data of the original leaf to the unused leaf on the right side of the rightmost used leaf.
@@
 If the used leaf is on the rightmost of the tree, it has to execute full copy.
-Therefore, make all the used leaves tightly packed together to the left side of the new order tree in the original order.
+Therefore, make all the used leaves tightly packed together to the left side of the new value-independent order tree in the original order.
 
 Fig.
-4 shows a series of execution of order tree.
+4 shows a series of execution of value-independent order tree.
 In this figure, full copy happens at the time when state 6 turns into state 7.
@@
   \includegraphics[width=0.4\textwidth]{../images/order-tree}
-  \caption{order tree with size 4}
+  \caption{value-independent order tree with size 4}
 \end{figure}
@@
   \includegraphics[width=0.4\textwidth]{../images/order-trees}
-  \caption{order tree multiple operation}
+  \caption{value-independent order tree multiple operation}
 \end{figure}
@@
 \subsubsection{complexity analysis}
-In the following analysis, the size of the order tree is $n$.
+In the following analysis, the size of the value-independent order tree is $n$.
 If full copy doesn’t happen, execution of get and put go through root to leaf two times.
-The height of the order tree is $O(\log n)$, and the time and space complexity are both $O(\log n)$.
+The height of the value-independent order tree is $O(\log n)$, and the time and space complexity are both $O(\log n)$.
 
-If full copy happens, it has to go through the order tree,
+If full copy happens, it has to go through the value-independent order tree,
 and has all used leaves congregate to form a new tree.
@@
 \item persistent hash table + persistent red-black tree
-\item persistent hash table + persistent order tree
+\item persistent hash table + persistent value-independent order tree
 \end{itemize}
@@
 Doubly-linked list, persistent red-black tree,
-persistent order tree are all implemented by ourselves.
+persistent value-independent order tree are all implemented by ourselves.
 
 From now on, we will refer to these three composite data structures
-as doubly linked list, red-black tree, and order tree.
+as doubly linked list, red-black tree, and value-independent order tree.
 
@@
 tree is rather gentle ($O(\log n)$).
-Noting that the line graph of the order tree,
+Noting that the line graph of the value-independent order tree,
 compared to the smooth growth of the red-black tree,
@@
 Because the number of leaves of the
-order tree is $1 + \lceil \log_2 n \rceil$,
+value-independent order tree is $1 + \lceil \log_2 n \rceil$,
 its number of leaves is more discrete,
@@
 From Fig 7 we can know that, when cache size is 30000,
-put rate is 100\%, hit rate is 1.0, order tree implementation
+put rate is 100\%, hit rate is 1.0, value-independent order tree implementation
 can process 1000 blocks in 1.241 seconds, that means 
@@
 We chose Merkle Patricia tree verification cost to compare
-with the order tree implementation,
+with the value-independent order tree implementation,
 We choose trie-db module,
@@
 
-The Experiments verify that order tree and red-black tree
+The Experiments verify that value-independent order tree and red-black tree
 have lower time complexity. When the cache size increases
@@
 doubly linked list in performance. Compared with
-red-black tree, order tree does not need to maintain
+red-black tree, value-independent order tree does not need to maintain
 the color of the node, and to execute various rotation rules,
@@
 we first try the combination of persistent hash table and persistent red-black trees,
-Further proposed a novel data structure, order tree, let it be combined with persistent hash,
+Further proposed a novel data structure, value-independent order tree, let it be combined with persistent hash,
 Get a more efficient implementation of persistent LRU.

### 2020-06-24 abstract.tex
小更正

@@
 它的每一筆交易中附上了合法性證明，
-使得節點不需要進入資料儲存裝置查找過往賬本資訊，
+使得節點不需要進入資料儲存裝置查詢過往賬本資訊，
 只要驗證交易內附的證明即可，
@@
 當快取數十個區塊大小的賬戶資訊量時，
-快取命中所需的查找時間仍數倍低於梅克爾 Patricia 證明驗證的時間。
+快取命中所需的查詢時間仍數倍低於梅克爾 Patricia 證明驗證的時間。
 
@@
 each node maintains a complete ledger which
-records entire transaction history of all accounts.
-Years after years, requirement to single node will
+records the entire transaction history of all accounts.
+Years after years, the requirement to a single node will
 get higher and higher. Dealing with the issue, stateless
@@
 to access the data storage device to search past information
-of the ledger. Instead, node only verifies the proof attached
+of the ledger. Instead, a node only verifies the proof attached
 to each transaction. Therefore, it will significantly
@@
 Second,
-there are so many cache replacement polcies.
-For LRU polices, we designed two composite data
+there are so many ceche replacement polcies.
+For LRU policies, we designed two composite data
 structures which based on red-black tree and value-independent order tree.

### 2020-07-23 abstract.tex
修正錯別字

@@
 
-在本論文中，我們將在基於賬號的區塊鏈上討論以下兩點：
+在本論文中，我們將在基於賬戶的區塊鏈上討論以下兩點：
 第一，
 一筆交易的合法性很可能由最近出現過的其他交易的合法性推知，
-只要快取賬號的訊息，
+只要快取賬戶的訊息，
 就可以省略部分交易的證明，
@@
 Second,
-there are so many ceche replacement polcies.
+there are so many cache replacement policies.
 For LRU policies, we designed two composite data

### 2020-08-12 abstract.tex
將 heap 移至正文並補圖

@@
 快取替換有多種策略，針對 LRU 策略，
-設計了基於不可變紅黑樹與不可變值無關順序樹的兩種資料結構，
+設計了基於不可變紅黑樹、不可變值無關順序樹、不可變堆積的三種資料結構，
 並且進行實驗比較了快取命中與快取失效的代價，
@@
 For LRU policies, we designed two composite data
-structures which based on red-black tree and value-independent order tree.
+structures which based on red-black tree, value-independent order tree and heap.
 And conduct some experiments to compare the cost of a

### 2020-08-24 abstract.tex
修正摘要

--- 2020-07-23 abstract.tex
@@
 快取替換有多種策略，針對 LRU 策略，
-設計了基於不可變紅黑樹與不可變值無關順序樹的兩種資料結構，
-並且進行實驗比較了快取命中與快取失效的代價，
+我們設計了基於不可變紅黑樹、不可變值無關順序樹、不可變堆積的三種資料結構，
+透過共享資料，它們的時空間複雜度都控制在合理的範圍。
+我們也進行實驗比較了快取命中與快取失效的代價，
 模擬現今以太坊的區塊性質，
@@
 there are so many cache replacement policies.
-For LRU policies, we designed two composite data
-structures which based on red-black tree and value-independent order tree.
-And conduct some experiments to compare the cost of a
+For LRU policies, we designed three composite data
+structures based on red-black tree, value-independent order tree, and heap.
+By sharing data, these data structures have feasible space complexity and time complexity.
+In our experiments, we compared the cost of a
 cache hit with the penalty of a cache miss.
-Simulating today's Ethereum's block property,
-when cache size can contain several tens of blocks' information,
-the cache searching time is significantly lower than
-the time to verify Merkle Patricia proofs.
+Simulating Ethereum's block property nowadays,
+if cache size is able to contain tens of blocks' information,
+the cache searching time will be significantly lower than
+the time of verifying Merkle Patricia proofs.
 
